\documentclass[letterpaper,11pt]{letter}

% Include necessary packages
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

% Set up page margins
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

% Customize section formatting
\usepackage{xcolor}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries\color{blue}}{}{0em}{}[\titlerule]

% Define your information
\def\yourname{Muhammad Saad Shafiq}
\def\youraddress{Lahore, Pakistan}
\def\youremail{muhammadsaadshafiq275@gmail.com}
\def\yourphone{+92-3167107392}
\def\todaydate{\today}
\def\companyname{PakWheels}
\def\position{Software Engineer }

\begin{document}

\begin{letter}{\companyname\\
                Lahore, Pakistan\\}

\opening{Dear Hiring Manager,}

\section*{Introduction}
I am writing to express my strong interest in the \position position at \companyname, as advertised on your company's website. With a solid background in computer science and hands-on experience in mobile development, I am confident in my ability to contribute effectively to your team.

\section*{Education}
I am a recent graduate from the National University of Computer and Emerging Sciences, where I earned a Bachelor of Science in Computer Science. My coursework included extensive studies in web programming, mobile development, software testing, and artificial intelligence.

\section*{Experience}
As a Research Assistant at FAST-NUCES, I had the opportunity to work on a significant project, "Emergency Expert." This project involved the development of a comprehensive healthcare tool, including a mobile app built with Android Studio and a web app using React. I successfully implemented features such as diagnostics, optimal hospital suggestions, bed and token management, and integrated pharmacy services, showcasing my ability to deliver impactful solutions.

My freelance experience in Flutter/Android development allowed me to specialize in creating visually appealing and user-friendly interfaces, implementing robust backend functionalities, and ensuring seamless app performance. Additionally, my expertise in web scraping and automation development has equipped me with valuable skills in data extraction, analysis, and visualization.

\section*{Projects}
In my projects, such as the "Token System App" and "Inventory Chat Bot," I demonstrated a strong understanding of mobile and web technologies. These experiences have honed my problem-solving abilities and creativity in developing innovative solutions.

\section*{Skills}
My programming skills include proficiency in Python, Java, Kotlin, Dart, and various technologies such as Android Studio, Flutter, and Selenium. I am adept at utilizing tools like Docker, GCP, and MongoDB to enhance the efficiency of development processes.

\section*{Conclusion}
I am excited about the opportunity to contribute to \companyname' software development team. My passion for creating impactful and user-centric applications, combined with my strong technical skills, makes me a perfect fit for this role.

Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences align with the needs of your team.

\closing{Sincerely,\\
\yourname \\
\youremail\\
\yourphone }

\end{letter}
\end{document}
